---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---

# Frame

1. Maximum number of tourists travelling to India are from which country?
2. Predict the number of tourists traveling to India for the year 2011 from 
   that country.
   
   
# Aquire

The data is in datafile.csv, aquired from https://data.gov.in/catalog/number-foreign-tourists-indi

```{r}
# Reading the csv to dataframe
df <- read.csv("datafile.csv")

# view the structure of dataframe
str(df)
View(df)

```

# Refine and Transform

- I will remove the rows with Others and Total in Nationality column
```{r}
library(dplyr)
library(tidyr)
df <- df %>%
    filter(Nationality != "Others", Nationality != "Total",
           Nationality != "STATELESS")
tail(df)
```

- Remove the Region column as we are only interested in Nationality

```{r}
df <- subset(df, select = -c(Region))
tail(df)

length(unique(df$Nationality))
str(df)

# Add summary column
df$summary = df$X2001 + df$X2002 + df$X2003 + df$X2004 + df$X2005 + df$X2006 +                      df$X2007 + df$X2008 + df$X2009 + df$X2010

# Arrange in descending order
df <- df %>% arrange(desc(summary))
dfTop10 <- df %>% top_n(10)
dfTop10
```

# Explore

Display bar chart of maximum number of tourists

```{r}
library(ggplot2)

countryBarPlot <- ggplot(dfTop10) + 
    aes(reorder(Nationality, summary), weight = summary, fill = summary) + 
    xlab("Country") +
    ylab("Number of Tourists") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
    geom_bar()
    

library(plotly)
ggplotly(countryBarPlot)

```

Answering the question: 

We can clearly see from the graph that maximum number of tourists are from **U.S.A.** in between the years 2001 to 2010, followed by **U.K.**

# Model

- Plot a scatter plot to view the relation

```{r}

usaData <- data.frame(year=c(2001:2010), tourists=as.numeric(dfTop10[1,2:11]))

p <- ggplot(usaData) +
    aes(year, tourists)
p + geom_point() 


```

- Try to fit linear regression 

```{r}
model1 <- lm(tourists~year, data = usaData)
model1
summary(model1)
# Notice that r2 is close to 1, so it looks like good fit

plot(tourists~year, data = usaData)
abline(model1, col = "red")

plot(model1)

# Predicting the values
p1 <- predict(model1, data.frame(year=c(2011:2014)))
predictedDf <- data.frame(year=2011:2014, tourists=p1)
predictedDf
```

- From **predictedDf** we can predict that **1016694** tourists are going to come to India from USA in the year 2011.

# Communicate

The following are the answers to the framed question:

1.  The maximum number of tourists are from **U.S.A.** in between the years 2001 to     2010, followed by **U.K.**

2.  **1016694** tourists are going to come to India from USA in the year 2011.

Do check out my github repo git@github.com:dalonlobo/art-of-datascience.git, for my other work in this field.
