---
title: "Analysis of Onion prices"
author: "Dalon Lobo"
date: "April 26, 2017"
output:
  html_document: default
  pdf_document: default
always_allow_html: yes
---

# Question

Analyse the Onion Price on State and Day Level. Solve the following 2 parts:

    1. Find the State with the highest quantity sales.
    2. Predict the daily price for the next 30 days for that state.
    
# Analysis

## Steps involved

The following general steps are involved in a typical analysis.

    1. Frame
    2. Acquire
    3. Refine
    4. Transform
    5. Explore
    6. Model
    7. Communicate
    
We will carry out the above steps and find the result.

# Acquire

Lets scrape the data from [NHRD site](http://nhrdf.org/en-us/DailyWiseMarketArrivals)

* I will use 'rvest' package to scrape the data
* I've chosen year 2017, Jan, Feb data for analysis
* After applying the filters in site, I've saved the html locally by name "DailyWiseMarketArrivals.html"

```{r Aquire}
library(rvest)
setwd("D:/GreatLakes/Res2")
pgOut <- read_html("DailyWiseMarketArrivals.html")
pgTable <- pgOut %>%
            html_node("#dnn_ctr966_DailyWiseMarketArrivals_GridView1") %>%
            html_table()

df <- pgTable
str(df)
```

# Refine

* Removing the last row, as it contains total, which we are not interested in.

```{r}
library(dplyr)
# using dplyr filter function to remove the row
colnames(df)
df <- df %>%
    filter(Market != "Total")
tail(df)

```

* Renaming the column names

```{r}
names <- c('date', 'state', 'quantity', 'minPrice', 'maxPrice', 'modPrice')
colnames(df) <- names
str(df)
```

* Changing the date to r date datatype

```{r}
df$date <- as.Date(df$date, "%d/%b/%Y")
df$minPrice <- as.numeric(df$minPrice)
df$maxPrice <- as.numeric(df$maxPrice)
df$modPrice <- as.numeric(df$modPrice)
str(df)
```

* Seperate out city and state

```{r}

library(stringr)
library(tidyr)
df <- df %>%
    mutate(state1 = state) %>%
    separate(state1, c("city", "stateAbbr"), sep="\\(")
head(df)
df$stateAbbr <- str_replace_all(df$stateAbbr, "\\)", "")

```

* Removing the rows with NA
```{r}
sum(is.na(df$stateAbbr))
df <- df[!(is.na(df$stateAbbr)), ]
sum(is.na(df$stateAbbr))
df <- df[, !duplicated(colnames(df))]
unique(df$stateAbbr)
```

# Transform

* Now lets group by state and find the state with highest quantity sales

```{r}
qTable <- df %>% 
    group_by(stateAbbr) %>% 
    summarise(quantityByState = sum(quantity)) %>% 
    arrange(desc(quantityByState)) %>%
    filter(quantityByState > 75000)
qTable[which.max(qTable$quantityByState),]

```

We can conclude that **MS - Maharastra** has the highest quantity sales i.e. **10915963(q)**

# Explore

```{r}
library(ggplot2)
statePlot <- ggplot(qTable) +
    aes(reorder(stateAbbr, quantityByState),
        weight = quantityByState,
        fill = quantityByState) +
    geom_bar() +
    coord_flip() +
    labs(y = "Quanity (q)",
        x = "State", title = "State Vs Quantity")

library(plotly)
ggplotly(statePlot)
```



You can clearly conclude from the graph that Maharastra is leading consumer of onions.

# Model 

Lets predict for next 30 days for state Maharastra

```{r}
dim(df)
str(df)
dfMS <- df %>%
  filter(stateAbbr == "MS") %>%
  select(date, modPrice) %>%
  arrange(date)
dim(dfMS)

ggplot(dfMS) + aes(date, modPrice) + geom_line() +
    labs(title = "Mod price Vs Date")



```

Lets use prophet library to predict the future prices

```{r}
library(prophet)
colnames(dfMS) <- c('ds', 'y')
str(dfMS)
m <- prophet(dfMS)

future <- make_future_dataframe(m, periods = 30, freq = 'd')
tail(future)

forecast <- predict(m, future)
tail(forecast[c('ds', 'yhat', 'yhat_lower', 'yhat_upper')])

plot(m, forecast,   xlab = "Date",
  ylab = "Price")

prophet_plot_components(m, forecast)

```

# Communicate / Conclusion

Using R, we have successfully scraped the data and predicted the prices for next 30 days.

Conclusion is as follows:

    *   Maharastra MS is the highest consumer of onions 10915963(q)
    *   The prediction is successfully ploted in the above graphs.










